Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-11 paper/paper.tex
Wording
Final touches. Add links to code and data.

\usepackage[pdftex]{hyperref}
\newcommand{\figref}[1]{\hyperref[#1]{Figure~\ref*{#1}}}
\newcommand{\secref}[1]{\hyperref[#1]{Section~\ref*{#1}}}
\newcommand{\tabref}[1]{\hyperref[#1]{Table~\ref*{#1}}}
\newcommand{\ea}{{et~al.}\xspace}

@@

@@

\figref{fig:confidence_approximate} shows the confidence of participants in their responses grouped by approximate and precise.

\begin{figure}[!t]
  \centering
  \includegraphics[width=0.8\columnwidth]{confidence}
  \caption{Relative counts of confidence in answers about the approximate and precise data. 1 is the lowest confidence, 7 the highest.}
  \label{fig:confidence}
\end{figure}

@@

>>>>

\usepackage[pdftex, colorlinks]{hyperref}
\newcommand{\figref}[1]{\hyperref[#1]{Figure~\ref*{#1}}}
\newcommand{\secref}[1]{\hyperref[#1]{Section~\ref*{#1}}}
\newcommand{\tabref}[1]{\hyperref[#1]{Table~\ref*{#1}}}
\newcommand{\ea}{{et~al.}\xspace}

@@

The study is online at \url{https://domoritz.github.io/bias-study/index.html}.

@@

We asked participants to report the confidence in their responses.
\figref{fig:confidence} shows the distribution of relative frequencies grouped by approximate and precise.

\begin{figure}[!t]
  \centering
  \includegraphics[width=\columnwidth]{confidence}
  \caption{Relative counts of confidence in answers about the approximate and precise data. 1 is the lowest confidence, 7 the highest.}
  \label{fig:confidence}
\end{figure}

@@

All material for this study, results, and the analysis are available at \url{https://github.com/domoritz/bias-study}.
